Constraint Programming - Inside Gecode

### 2014-05-06 paper.tex
made squares to the introduction example

	\section{Introduction}
	Constraint programming is a method to solve mathematical problems through the formulation of constraints, which describe the desired solution. As a formal and exact definition, like it can be found in \cite[p.~16]{handbookCP} for constraint programming, is not as helpful as an example, I would like to give you a short overview on the topic through the problem called \emph{SEND MORE MONEY}.

	Consider the problem of choosing how many components of three different types should be placed on a chip where variables $x$, $y$ and $z$ represent the number of components for each type. As the size of the chip is limited the total area is constrainted by
	\begin{equation}
		10x + 15y + 5z \le 1000
		\label{eq:areaConstraint}
	\end{equation}
	with different weights for each type. Additionally, the types have different costs and the total cost for a chip is limited:
	\begin{equation}
		3x + y^2 + 2z \le 500
		\label{eq:costConstraint}
	\end{equation}
	The target for this problem could be maximization of the price at which the chip can be sold:
	\begin{equation}
		\max_{x, y, z} 5x + 6\ln(y) + z
		\label{eq:objective}
	\end{equation}

	A solver for constraint programming like \emph{Gecode} provides the necessary tools to define constraints like \refeq{eq:areaConstraint}, \refeq{eq:costConstraint} and \refeq{eq:objective} in their most natural form as equations and inequations and will find all possible solutions or just one of them, depending on the selected algorithm. If there would be only linear constraints like \refeq{eq:areaConstraint} it would be possible to solve this problem through linear programming \cite[1]{linearProgramming}. As linear programming is only a subset of constraint programming the latter one is the more general one with more practical applications; not every problem in the real world is linear or can be linearized in a useful way. Consequently, constraint programming with its ability to consider constraints in their most general form can be used in various fields like scheduling of resources, computer-aided design and robotics \cite[p.~221]{trendsInCP}.

@@

	As constraint programming is the generalization of linear programming it is at least possible do define linear constraints like \refeq{eq:linearConstraint}. Which statements are possible to make and how handy it is to do so varies very much from the programming language in which the problem is implemented and the used toolset. Typical constraints are the following
	\begin{itemize}
		\item Equalities: $x = y + 2$, $x^2 + y^2 = 1$, \dots
		\item Inequalities: $x \ne y$, \dots
		\item Relations: $x < 2 y$, $e^x < 4$, \dots
	\end{itemize}

	Different constraint types like equalities and inequalities can be combined through logical operators to boolean expressions. To show the usage of this on an example I will give the implementation for the placement of two squares such that they do not overlap. The related variables are defined in \reffig{fig:squares}. This problem can be expressed by \cite[p. 101]{programmingGecode}
	\begin{equation}
	\begin{split}
		x_1 + d_1 \le x_2 & \lor x_2 + d_2 \le x_1 \lor \\
		y_1 + d_1 \le y_2 & \lor y_2 + d_2 \le y_1
	\end{split}
	\end{equation}

>>>>

	\section{Introduction}
	Constraint programming is a method to solve mathematical problems through the formulation of constraints, which describe the desired solution. As a formal and exact definition, like it can be found in \cite[p.~16]{handbookCP} for constraint programming, is not as helpful as an example, I would like to give you a short overview on the topic through the problem of the placement of two squares such that they do not overlap.

	The related variables for this example are defined in \reffig{fig:squares}. The problem can be expressed by \cite[p. 101]{programmingGecode}
	\begin{equation}
	\begin{split}
		x_1 + d_1 \le x_2 & \lor x_2 + d_2 \le x_1 \lor \\
		y_1 + d_1 \le y_2 & \lor y_2 + d_2 \le y_1
	\end{split}
	\label{eq:squares}
	\end{equation}
	The task for the constraint programming tool at this point is then to find feasible solutions which fulfill the constraints.

	A solver for constraint programming like \emph{Gecode} provides the necessary tools to define constraints like \refeq{eq:squares} in their most natural form as equations and inequations and will find all possible solutions or just one of them, depending on the selected algorithm. If there would be only linear constraints like \refeq{eq:squares} it would be possible to solve this problem through linear programming \cite[1]{linearProgramming}. As linear programming is only a subset of constraint programming the latter one is the more general one with more practical applications; not every problem in the real world is linear or can be linearized in a useful way. Consequently, constraint programming with its ability to consider constraints in their most general form can be used in various fields like scheduling of resources, computer-aided design and robotics \cite[p.~221]{trendsInCP}.

@@

	As constraint programming is the generalization of linear programming it is at least possible do define linear constraints like \refeq{eq:squares}. Which statements are possible to make and how handy it is to do so varies from the programming language in which the problem is implemented and the used toolset. Typical constraints are
	\begin{itemize}
		\item Equalities: $x = y + 2$, $x^2 + y^2 = 1$, \dots
		\item Inequalities: $x \ne y$, \dots
		\item Relations: $x < 2 y$, $e^x < 4$, \dots
	\end{itemize}
